### 2015-01-14 paper.tex
more text

% \begin{verbatim}
 \begin{lstlisting}
data Rule = Remove [Tag] Condition | Select [Tag] Condition deriving (Show)

-- | There is no special constructor for empty condition (ie. remove/select tag everywhere),
-- | but `C _ []' is assumed to mean that.
data Condition = C Position [Tag]
               | NOT Condition
               | AND Condition Condition
               | OR Condition Condition deriving (Show)

-- | Position can be exact or at least.
-- | The meaning of numbers is 
-- | *  0: word itself
-- | * -n: to the left
-- | *  n: to the right.
data Position = Exactly Integer | AtLeast Integer deriving (Show,Eq,Read)
 \end{lstlisting}
%\end{verbatim}

>>>>

% \begin{verbatim}
 \begin{lstlisting}
data Rule = Remove [Tag] Condition | Select [Tag] Condition

data Condition = C Position [Tag]
               | NOT Condition
               | AND Condition Condition
               | OR Condition Condition 
\end{lstlisting}

The data type for Rule is either remove or select a list of tags, with condition(s).
For Condition, there are basic conditions (position and a list of context tags) and combined conditions, with constructors `NOT', `AND' and `OR'. For instance, the following rule is read as ``remove tag for any verb, if the lemma is \emph{bear} or there is a determiner or an article anywhere to the left''.

\begin{lstlisting}
verb = [V, V2, V3, VV, V2V, VS]
Remove verb (OR (C (Exactly 0)  [Lem "bear"])
                (C (AtLeast -1) [Det,Art])
            )
\end{lstlisting}

There is no special constructor for empty condition (ie. remove/select tag everywhere), but an empty tag list in a condition, i.e. \texttt{C \_ []} is assumed to mean that.

The data type for position can be exact n places or at least n places. The number 0 means the word itself, negative number means \emph{n} positions to the left and positive \emph{n} positions to the right.

\begin{lstlisting}
data Position = Exactly Integer | AtLeast Integer
 \end{lstlisting}
